---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

## What can bathymetry data tell us about conventional lake depth data and predictive models?

### Products

Data Summary: [manuscript/data.pdf](manuscript/data.pdf)

Figures: [manuscript/figures.pdf](manuscript/figures.pdf)

Tables: [manuscript/tables.pdf](manuscript/tables.pdf)

Data: [bathymetry derived lake depth](data/00_bathy_depth/00_bathy_depth.csv)

<details>
<summary>Data dictionary</summary>
```{r, echo=FALSE}
# see scripts/99_make_taxonomy.R

dt <- read.csv("data/00_bathy_depth/00_bathy_depth.csv", stringsAsFactors = FALSE)
knitr::kable(setNames(data.frame(names(dt)), "field")) 
```
</details> &nbsp;

Data: [bathymetry derived lake geometry](data/00_bathy_depth/bathy_geometry.csv)

<details>
<summary>Data dictionary</summary>
```{r, echo=FALSE}
# see scripts/99_make_taxonomy.R

dt <- read.csv("data/00_bathy_depth/bathy_geometry.csv", stringsAsFactors = FALSE)
knitr::kable(setNames(data.frame(names(dt)), "field"))
```
</details>
