---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

## LAGOS-US-Depth: Lake depth at continental scales

[![Paper DOI](https://img.shields.io/badge/Paper-DOI-blue.svg)]() [![Code DOI](https://zenodo.org/badge/123951266.svg)](https://zenodo.org/badge/latestdoi/123951266)

### Data (see [data/lagosus_depth.csv]())

```{r echo=FALSE}
# see scripts/99_make_taxonomy.R

dt <- read.csv("data/lagosus_depth_taxonomy.csv", stringsAsFactors = FALSE)

knitr::kable(setNames(dt, c("Variable name", "Description")))
```

### Products

Figures: [manuscript/figures.pdf](manuscript/figures.pdf)

Appendix: [manuscript/appendix.pdf](manuscript/figures.pdf)

### Abstract

Lake depth is widely regarded as a critical predictor of nutrient cycling in lakes. Unfortunately, existing databases lack widespread information on this basic measure. Lack of depth data is a key impediment to effective lake nutrient prediction in thousands of lakes at regional to continental scales. Although a number of investigators have developed predictive models of lake depth based on topography surrounding a lake, predictions from such models have proved to be fairly imprecise. To improve prediction of lake depth, we compiled a database of maximum depth for more than 15,000 lakes throughout the conterminous United States and used it to develop predictive models of lake depth based on factors such as lake elevation, topography, geometry, impoundment status, and landform. We used fitted models to predict lake depth for nearly all lakes in the conterminous United States and show how our statistical models, which are stratified on lake and watershed characteristics, represent an improvement over existing models. Ultimately, our lake depth predictions could be used not only as an aid in predicting lake nutrients but also as a rough check on estimates of total lake volume used in Earth System Models.
