---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

## Bathymetry data from thousands of lakes show that difficulty modeling in-lake slope limits lake depth prediction

### Products

Data Summary: [manuscript/data.pdf](manuscript/data.pdf)

Figures: [manuscript/figures.pdf](manuscript/figures.pdf)

Tables: [manuscript/tables.pdf](manuscript/tables.pdf)

Data: [bathymetry derived lake depth](data/00_bathy_depth/00_bathy_depth.csv)

<details>
<summary>Data dictionary</summary>
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# see scripts/99_make_taxonomy.R
library(dplyr)
taxonomy <- read.csv("data/taxonomy.csv", 
                     stringsAsFactors = FALSE)
dt       <- read.csv("data/00_bathy_depth/00_bathy_depth.csv", 
               stringsAsFactors = FALSE) %>%
  names() %>%  as.data.frame() %>%  setNames("col_name") %>%
  left_join(taxonomy)
knitr::kable(dt) 
```
</details> &nbsp;

Data: [bathymetry derived lake geometry](data/depth_predictors.csv)

<details>
<summary>Data dictionary</summary>
```{r, echo=FALSE}
# see scripts/99_make_taxonomy.R

dt <- read.csv("data/depth_predictors.csv", stringsAsFactors = FALSE)
knitr::kable(setNames(data.frame(names(dt)), "field"))
```
</details>
